Demystifying the Combination of Dynamic Slicing and \\ Spectrum-based Fault Localization

### 2019-02-26 paper/ijcai/paper.tex
another pass on RQ3

A necessary but insufficient condition for improvement of fault
localization with \comb{} is that dynamic slicing eliminates a high
amount of code from the best ranked files. Table \ref{tab:red} shows,
as percentages, the size reduction of the top files obtained with
dynamic slicing for different values of $k$. Overall, results indicate
that dynamic slicing substantially reduces the size of highly-ranked
files. \Mar{+ coverage?}

@@

In \textbf{RQ3}, we evaluate the impact of combining \ds{} with \sfl{}
to improve fault localization. The first experiment we ran consists of
measuring the \emph{difference of diagnosis cost} between the two
fault localization techniques. This metric has been previously used in
other
studies~\cite{7390282,ang-perez-van-deursen-rui-2017,Pearson:2017:EIF:3097368.3097441,Perez:2018:LQR:3304889.3304927}.
More specifically, we computed $\Delta{}C = C(\textrm{SFL$^{k}$}) -
C(\textrm{\combpar{k}})$, where $C$ denotes the diagnosis cost and is
obtained by computing the mean position in the ranking of all buggy
statements. $\Delta C >0$ means that \combpar{k} outperformed the
baseline, \ie{} the mean position of the faulty statements is smaller
in \combpar{k} compared to that of the baseline. $\Delta C <0$ means
that \combpar{k} performs worse compared to its baseline. That could
happen if dynamic slicing misses the faulty statement. $\Delta C=0$
means that the faulty statement remained in the same position.  It is
worth noting that we assume perfect bug
understanding~\cite{Parnin:2011:ADT:2001420.2001445}, i.e., if the
developer sees the bug in the ranking, he is able to precisely
determine if it is the faulty one.

@@

Figure \ref{fig:diagnosis} summarizes performance of \combpar{k}
relative to \sfl{}$^{k}$. The figure shows a histogram over
$\Delta{}C$ for different values of $k$. Note that (1) the number of
cases where the baseline outperforms \combpar{k} is small (\eg{},
\numOutPerformed\ of the \numFaults\ faults for $k=10$) and that (2)
the number of cases \combpar{k} outperforms the baseline is
significative (\eg{}, $117$ of the \numFaults\ faults for $k=10$). One
of the following reasons justifies the baseline outperforming
\combpar{k}:\Mar{following sentence is confusing IMO. suggest to
  clarify or remove. aren't points two and three equivalent? as for
  one, isn't foo an issue both for \combpar{k} and \sfl{}$^{k}$?} (1)
a fault of omission, (2) the test has design limitations which \ds~is
not capable of handling, or (3) the buggy-class in not in the top $k$
of the highest-ranked faulty classes under analysis.

@@

Table \ref{table:st}
presents the statistics to determine if the observed results are
statistically significant. Shapiro-Wilk tests the null hypothesis that
results are drawn from a normal distribution. The test is perfomed for
all techniques and its variants. With $99\%$ of confidence, the
results tell us that the distributions are not normal. Given that $C$
is not normally distributed, we use Friedman test, a non-parametric
statistical test of hypothesis. The null hypothesis is that the
ranking results of all techniques and variants are the same. With
$99\%$ confidence, the results show that the distributions are
distinct. To understand which techniques perform differently, \ie{} to answer
the question \textit{Does \combpar{k} perform differently than
\sfl{}$^{k}$}, we performed a Siegel post-hoc analysis. Figure
\ref{fig:performance} reports the results of Siegel analysis for all
pairs of techniques. Each square represents the
statistical significance of the diagnostic accuracy amongst the different
techniques, i.e., if it is significant it means that the techniques perform
differently. We can determine with $95\%$ confidence that the
performance of each pair of techniques is different.

@@

As the results are statistically significant, it is possible to state that \combpar{k}
has a positive effect on the localization of some types of bugs. There is indeed a
problem on using slicing on fault of omission bugs that needs further research.
Although, this dataset has more than $50\%$ of fault of omissions, our
simple slicing approach was capable of improving the ranking of $95$ faults for $k=5$
and $115$ faults for $k=10$. These are promissing results from what Automated
Program Repair techniques may directly benefit to improve the accuracy of their own
techniques.

>>>>

A necessary but insufficient condition for improvement of fault
localization with \comb{} is that dynamic slicing eliminates a high
amount of code from the best ranked files. Table \ref{tab:red} shows,
as percentages, the size reduction of the top files obtained with
dynamic slicing for different values of $k$. Overall, results indicate
that dynamic slicing substantially reduces the size of highly-ranked
files.

%\Mar{+ coverage?}

@@

@@

In \textbf{RQ3}, we evaluate the impact of combining \ds{} with \sfl{}
to improve fault localization. The first experiment we ran consists of
measuring the \emph{difference of diagnosis cost} between the two
fault localization techniques. This metric has been previously used in
other
studies~\cite{7390282,ang-perez-van-deursen-rui-2017,Pearson:2017:EIF:3097368.3097441,Perez:2018:LQR:3304889.3304927}.
More specifically, we computed $\Delta{}C = C(\textrm{SFL$^{k}$}) -
C(\textrm{\combpar{k}})$, where $C$ denotes the diagnosis cost and is
obtained by computing the mean position in the ranking of all buggy
statements. $\Delta C <0$ means that \combpar{k} performs worse
compared to its baseline. That could happen if dynamic slicing misses
the faulty statement. $\Delta C=0$ means that the faulty statement
remained in the same position. $\Delta C >0$ means that \combpar{k}
outperformed the baseline, \ie{} the mean position of the faulty
statements is smaller in \combpar{k} compared to that of the
baseline. It is worth noting that we assume perfect bug
understanding~\cite{Parnin:2011:ADT:2001420.2001445}, i.e., if the
developer sees the bug in the ranking, he is able to precisely
determine if it is the faulty one.  Figure \ref{fig:diagnosis}
summarizes the performance of \combpar{k} relative to
\sfl{}$^{k}$. The figure shows a histogram over $\Delta{}C$ for
different values of $k$. Note that (1) the number of cases where the
baseline outperforms \combpar{k} is small (\eg{}, \numOutPerformed\ of
the \numFaults\ faults for $k=10$) and that (2) the number of cases
\combpar{k} outperforms the baseline is significative (\eg{}, $117$ of
the \numFaults\ faults for $k=10$).

%% One
%% of the following reasons justifies the baseline outperforming
%% \combpar{k}:\Mar{following sentence is confusing IMO. suggest to
%%   clarify or remove. aren't points two and three equivalent? as for
%%   one, isn't foo an issue both for \combpar{k} and \sfl{}$^{k}$?} (1)
%% a fault of omission, (2) the test has design limitations which \ds~is
%% not capable of handling, or (3) the buggy-class in not in the top $k$
%% of the highest-ranked faulty classes under analysis.

@@

Table \ref{table:st} presents the statistics to determine if the
observed results are statistically significant. Shapiro-Wilk tests the
null hypothesis that results are drawn from a normal distribution. The
test is perfomed for all techniques and its variants. With $99\%$ of
confidence, the results tell us that the distributions are not
normal. Given that $C$ is not normally distributed, we use Friedman, a
non-parametric statistical test of hypothesis. The null hypothesis is
that the ranking results of all techniques and variants are the
same. With $99\%$ confidence, the results show that the distributions
are distinct. To understand which techniques perform differently,
\ie{}, to answer the question \textit{Does \combpar{k} perform
  differently than \sfl{}$^{k}$}, we performed a Siegel post-hoc
analysis. Figure \ref{fig:performance} reports results. Each square
shows the statistical significance of the difference in diagnostic
accuracy amongst the different techniques--the lighter color and
smaller value of $p$ indicates higher significance. Based on these
results, it is possible to determine with $95\%$ confidence that the
performance of each pair of techniques is different.

@@

As the results are statistically significant, it is possible to state
that \combpar{k} has a positive effect on the localization of some
types of bugs. There is indeed a problem on using slicing on fault of
omission bugs that needs further research.  Although, this dataset has
more than $50\%$ of fault of omissions, our simple slicing approach
was capable of improving the ranking of $95$ faults for $k=5$ and
$115$ faults for $k=10$. \Mar{Sofia, acho mais apropriado colocar isto
  em conclusions}These are promissing results from what Automated
Program Repair techniques may directly benefit to improve the accuracy
of their own techniques.
